---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# appsheet

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/calderonsamuel/appsheet/branch/main/graph/badge.svg)](https://app.codecov.io/gh/calderonsamuel/appsheet?branch=main)
[![R-CMD-check](https://github.com/calderonsamuel/appsheet/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/calderonsamuel/appsheet/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of appsheet is to provide an easy way to use the Appsheet API to retrieve, add, update and delete rows from your app tables. 

The package exports a main function called `appsheet()`, which you can use to perform all the supported actions. A supporting `ash_properties()` function allows you to customize the expected input/output.

Have in mind that there is no evidence that the API will also work well with *slices* and that `appsheet()` returns all the columns as *character* vectors.

## Installation

You can install the development version of appsheet from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("calderonsamuel/appsheet")
```

## Authentication

The first step is to [Enable the API for cloud-based service communication](https://support.google.com/appsheet/answer/10105769?hl=en&ref_topic=10105767&sjid=7476345061548698748-SA). Once this is done you should have:

1. The App ID. Use it in the `appId` argument of `appsheet()` or via the `APPSHEET_APP_ID` environmental variable.
2. The Application Access Key. Use it in the `access_key` argument of `appsheet()` or via the `APPSHEET_APP_ACCESS_KEY` environmental variable.

The `appsheet()` function looks for both environmental variables by default.

## Example

Here are some examples on how to perform the four basic operations. It all starts with loading the package.

```{r example}
library(appsheet)
```

### Read a table

The first argument of `appsheet()` is a table name. By default, `appsheet()` will use the "Find" action, which reads all the rows. The following code is the equivalent of using `appsheet(tableName = "Driver", Action = "Find")`.

```{r}
appsheet("Driver")
```

When the action is "Find", you can take advantage of the `Selector` argument of `ash_properties()`, which can use some AppSheet internal functions to narrow the output.

```{r}
appsheet(
	tableName = "Driver", 
	Properties = ash_properties(Selector = 'Filter(Driver, [Key] = "70608c66")')
)
```

### Add records to a table 

The "Add" action allows to add one or multiple records to a table. You must provide `Rows`, which can be a dataframe with the same column names as the specified table. You don't need to provide all the columns to be successful, but can't exclude the ones *required* by your app. Also, don't try to add the `_RowNumber`(or `Row ID` when using an AppsSheet database), as it is generated internally.

An "Add" action returns a data.frame with the added rows when successful.

```{r}
row_key <- paste0(sample(letters, 8), collapse = "") # to be reused 

appsheet(
	tableName = "Driver",
	Action = "Add",
	Rows = tibble::tibble(
		Key = row_key, # required in app logic
		`Email` = "driverXX@company.com" # required in app logic
	) 
)
```

### Update records from a table

The "Edit" action allow to update values from one or multiple records from a table, it also can target multiple columns. This one also requires the `Rows` argument. Again, you can't use the `_RowNumber` column (but in this one you can use the `Row ID` generated by an Appsheet database).

An "Edit" action returns a data.frame with the whole content of the updated rows when successful.

```{r}
appsheet(
	tableName = "Driver",
	Action = "Edit",
	Rows = tibble::tibble(
		Key = row_key,
		`Driver Name` = "Some name",
		Photo = "some/path.jpg"
	) 
)
```


### Delete records from a table

The "Delete" action allows to delete one or multiple records from a table. This one also requires the `Rows` argument. Again, you can't use the `_RowNumber` column (but in this one you can use the `Row ID` generated by an Appsheet database).

A "Delete" action returns a data.frame with the deleted rows when successful.

```{r}
appsheet(
	tableName = "Driver",
	Action = "Delete",
	Rows = tibble::tibble(
		Key = row_key
	) 
)
```









