---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# appsheet

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/calderonsamuel/appsheet/branch/main/graph/badge.svg)](https://app.codecov.io/gh/calderonsamuel/appsheet?branch=main)
[![R-CMD-check](https://github.com/calderonsamuel/appsheet/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/calderonsamuel/appsheet/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of appsheet is to provide an easy way to use the Appsheet API to retrieve, add, update and delete rows from your app tables. The package exports a single function called `appsheet()`, which you can use to perform all the supported actions.

## Installation

You can install the development version of appsheet from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("calderonsamuel/appsheet")
```

## Authentication

The first step is to [Enable the API for cloud-based service communication](https://support.google.com/appsheet/answer/10105769?hl=en&ref_topic=10105767&sjid=7476345061548698748-SA). Once this is done you should have:

1. The App ID. Use it in the `appId` argument of `appsheet()` or via the `APPSHEET_APP_ID` environmental variable.
2. The Application Access Key. Use it in the `access_key` argument of `appsheet()` or via the `APPSHEET_APP_ACCESS_KEY` environmental variable.

The `appsheet()` function looks for both environmental variables by default.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(appsheet)

# Find all the content of the "Driver" table
appsheet("Driver")
```


